partial: An R Package for Creating Partial Dependence Plots

### 2016-08-11 manuscript/greenwell.tex
minor edits

To illustrate, we will use the Los Angeles ozone pollution data described in ????. The data are available from \url{http://statweb.stanford.edu/~tibs/ElemStatLearn/datasets/LAozone.data}. The following code chunk loads the data into R:
\begin{example}
ozone <- read.csv(paste0("http://statweb.stanford.edu/~tibs/ElemStatLearn/",
                         "datasets/LAozone.data"), header = TRUE)
\end{example}

Next, we use MARS to to study the relationship between atmospheric ozone (\code{ozone}) concentration and meteorology in the Los Angeles basin in 1976, allowing for up to three-way interactions.
\begin{example}
ozone.earth <- earth(ozone ~ ., data = ozone, degree = 3)
summary(ozone.earth)
\end{example}
A single three-way interaction term between \code{wind}, \code{temp}, and \code{dpg} was selected by the MARS algorithm. To understand this interaction, we can use partial. However, since the partial dependece between three continuous variables can be computationally expensive, we will run \code{partial} in parallel.

>>>>

To illustrate, we will use the Los Angeles ozone pollution data described in \citet{breiman-1985-estimating}. The data contain daily measurements of ozone concentration (\code{ozone}) along with eight meteorological quantities for 330 days in the Los Angeles basin in 1976. The data are available from \url{http://statweb.stanford.edu/~tibs/ElemStatLearn/datasets/LAozone.data}. Details, including variable information, are available from \url{http://statweb.stanford.edu/~tibs/ElemStatLearn/datasets/LAozone.info}. The following code chunk loads the data into R:
\begin{example}
ozone <- read.csv(paste0("http://statweb.stanford.edu/~tibs/ElemStatLearn/",
                         "datasets/LAozone.data"), header = TRUE)
\end{example}

Next, we use MARS to to study the relationship between atmospheric ozone (\code{ozone}) concentration and meteorology in the Los Angeles basin in 1976, allowing for up to three-way interactions.
\begin{example}
ozone.earth <- earth(ozone ~ ., data = ozone, degree = 3)
summary(ozone.earth)
\end{example}
The model produced a generalized $R^2$ of $0.788$, similar to what was reported in \citet{breiman-1985-estimating}. A single three-way interaction was found involving the predictors
\begin{itemize}
  \item \code{wind}: wind speed (mph) at Los Angeles International Airport (LAX)
  \item \code{temp}: temperature ($^oF$) at Sandburg Air Force Base
  \item \code{dpg}: the pressure gradient (mm Hg) from LAX to Dagget, CA
\end{itemize}
To understand this interaction, we can use a partial plot. However, since the partial dependece between three continuous variables can be computationally expensive, we will run \code{partial} in parallel.
